### 2018-03-26 tex/paper.tex
revised abstract

Blockchains allow the specification of contracts in the form of programs that guarantee their fulfilment. 
Nevertheless, errors in those programs can cause important, and often irreversible, economical loses. General purpose 
languages tend to be unsuitable for this end, since their behaviour in exceptional situations tends to be hard to 
predict, and they are difficult to analyse due to their generality (they are usually turing-complete).

This paper explores the design of a domain specific language, Marlowe, targeted at the execution of financial 
contracts in the style of Peyton Jones on blockchains. We have focused on predictability, enforceability, simplicity, 
and ease of analysis and use.

>>>>

Blockchains allow the specification of contracts in the form of programs that guarantee their fulfilment. 
Nevertheless, errors in those programs can cause important, and often irretrievable, monetary loss. General-purpose languages provide a platform on which contracts can be built, but by their very generality they have the potential to exhibit behaviours of an unpredictable kind, and are also not easy to read or comprehend for general users.

An alternative solution is provided by domain-specific languages (DSLs), which are designed to express programs in a particular field. This paper explores the design of one DSL, Marlowe, targeted at the execution of financial 
contracts in the style of Peyton Jones \emph{et al} on blockchains. We have focused on predictability, enforceability, simplicity, 
and ease of analysis and use.
